### 2014-05-09 ms/ms.Rmd
added first trial of citations using knitcitations package

@@

@@

1. Our entire workflow is scripted, using the `R` computing environment. The database can be rebuilt in an instant from the raw datafiles, using a single command. When a single data contribution has been modified, the final master dataset is thus easily recreated.
2. We wrote a new `R` package [dataMashR](https://github.com/dfalster/dataMashR) for merging data from different studies in a transparent and reproducible fashion. While it was written with BAAD in mind, the package is designed to be easily  deployed for other compilations.
3. We used version control and the code sharing website [github](www.github.com) to track the evolution of the database and the code to process the raw data. Datasets as well as processing methods inevitably contain errors. With version control, we are able to trace these errors to the source. 
4. We used the package `knitr` within `R` to automatically produce reports comparing the raw data provided by a single study to the rest of the database. These reports were sent to data contributors for verification, and allowed easy identification of errors in the raw data or processing.

@@

>>>>

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
library(bibtex)
library(knitcitations)
```

@@

```{r, eval=FALSE, echo=FALSE}
#these commands below from package knitcitations work if you knit the file from within RStudio (being in the right ms directory), but they do not work when you generate the file using make.
#not working
#citep(c(Falster2011="10.1111/j.1365-2745.2010.01735.x"))
#citep(citation("base"))
#r citet("https://github.com/dfalster/dataMashR")
```

@@

1. Our entire workflow is scripted, using the R computing environment. The database can be rebuilt in an instant from the raw datafiles, using a single command. When a single data contribution has been modified, the final master dataset is thus easily recreated.
2. We wrote a new `R` package [dataMashR](https://github.com/dfalster/dataMashR) for merging data from different studies in a transparent and reproducible fashion. While it was written with BAAD in mind, the package is designed to be easily  deployed for other compilations.
3. We used version control and the code sharing website [github](www.github.com) to track the evolution of the database and the code to process the raw data. Datasets as well as processing methods inevitably contain errors. With version control, we are able to trace these errors to the source. 
4. We used the package `knitr` within `R` to automatically produce reports comparing the raw data provided by a single study to the rest of the database. These reports were sent to data contributors for verification, and allowed easy identification of errors in the raw data or processing.

@@

## REFERENCES
```{r, echo=FALSE, results='asis'}
bibliography(ordering = c("authors", "year", "title", "journal", "volume", "number", "pages", "url"))
```
